Learning Discrete Bayesian Networks from Continuous Data

### 2015-12-02 BN_discretizer_paper.tex

\subsection{Example 1}
The Bayesian network structure in Figure~\ref{fig:auto_graph_3} and the discretization results in Table~\ref{table:auto_disc_table_3} demonstrate that the MDL method does not always produce fewer discretization intervals than the Bayesian approach and that the MDL method can produce discretization policies with comparable likelihood.
The Bayesian network in Figure~\ref{fig:auto_graph_3} was obtained by running Algorithm~\ref{alg:structure_learn} fifty times on the Auto MPG dataset with a maximum of two parents per variable.
The network is better-structured than the one in Figure~\ref{fig:auto_graph_1} because the discretization policies were simultaneously learned with the network structure.
Many edges appear in both discretization results and are bolded in Table~\ref{table:auto_disc_table_3}.

>>>>

\subsection{Example 1}
The Bayesian network structure in Figure~\ref{fig:auto_graph_3} and the discretization results in Table~\ref{table:auto_disc_table_3} demonstrate that the MDL method does not always produce fewer discretization intervals than the Bayesian approach and that the MDL method can produce discretization policies with comparable likelihood.
The Bayesian network in Figure~\ref{fig:auto_graph_3} was obtained by running Algorithm~\ref{alg:structure_learn} fifty times on the Auto MPG dataset with a maximum of two parents per variable.
The network is structured more favorably with regards to discretization than the network in Figure~\ref{fig:auto_graph_1}, as the discretization policies were simultaneously learned with the network structure, resulting in higher data likelihood.
Many edges appear in both discretization results and are bolded in Table~\ref{table:auto_disc_table_3}.
